---
title: "PSOC_analysis"
author: "Maitri Jain"
date: '2023-02-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## checking overall significance of model
## checking if it explains big enough variance
## significant outliers
## model diagnostics - for generalizaiton purposes
## jn estimate
## both standardized and non-standardized effect sizes
## apa tables
## look at bootstrapped confidence intervals -- results same? testing for normality of residuals.


# Libraries and data
```{r}
library(tidyverse)
library(broom)
library(interactions)
library(psych)
library(corrplot)
library(Hmisc)
library(MVN)
library(sjPlot) # tables
library (car)

source("../../ISDP:SRCD 2022/R_Scripts/processv41/PROCESS v4.1 for R/process.R") 
df = read_csv("../data/PSOC_final_data.csv")

# Standardizing
df$PSOC_avg_z <- as.numeric(scale(df$PSOC_avg, center = TRUE, scale = TRUE))
df$PHQ9_total_z <- as.numeric(scale(df$PHQ9_total, center = T, scale = T))
df$SSQSR_SatisfactionAvg_z <- as.numeric(scale(df$SSQSR_SatisfactionAvg, center = T, scale = T))
df$childAge_z <- as.numeric(scale(df$childAge, center = T, scale = T))
df$numChildren_z <- as.numeric(scale(df$numChildren, center = T, scale = T))
df$HouseholdIncome_z <- as.numeric(scale(df$HouseholdIncome, center = T, scale = T)) 


```


# DESCRIPTIVE STATISTICS
```{r}
# Child Age
summary(df$childAge)
ggplot(df, aes(x = childAge)) + geom_freqpoly()
shapiro.test(df$childage_z) # not normal

# Race
summary(as.factor(df$ParentRace_string))
ggplot(df, aes(x = ParentRace_string)) + geom_bar()

# Ethnicity


# Income
summary(df$HouseholdIncome)
ggplot(df, aes(x = HouseholdIncome)) + geom_freqpoly()


# Education


# Number of children


# Parent age
summary(df$ParentAge)
ggplot(df, aes(x = ParentAge)) + geom_freqpoly()

# Parent gender
summary(as.factor(df$ParentGender))
ggplot(df, aes(x = ParentRace_string)) + geom_bar()

# PSOC
summary(df$PSOC_avg_z)
ggplot(df, aes(x = PSOC_avg_z)) + geom_histogram()
shapiro.test(df$PSOC_avg_z) # normal

# PHQ
summary(df$PHQ9_total_z)
ggplot(df, aes(x = PHQ9_total_z)) + geom_histogram()
shapiro.test(df$GAD_total_z) # not normal

# Social support total
summary(df$SSQSR_total_z)
ggplot(df, aes(x = SSQSR_total_z)) + geom_histogram()
shapiro.test(df$SSQSR_total_z) # not normal

# Social support satisfaction
summary(as.numeric(df$SSQSR_satisfaction_z))
ggplot(df, aes(x = as.numeric(df$SSQSR_satisfaction_z))) + geom_histogram()
shapiro.test(as.numeric(df$SSQSR_satisfaction_z)) # not normal

```

# Descriptive relationship between variables
```{r}
cor_data = df2 %>% select("childAge_z", "HouseholdIncome_z", "numChildren_z", "PSOC_avg_z", "PHQ9_total_z", "SSQSR_Total_z", "SSQSR_SatisfactionAvg_z")

# relationship between variables
pairs.panels(cor_data, method = "pearson")

# correlations between variables
correlations = rcorr(as.matrix(cor_data))
corrplot(correlations$r) 

```

# Multivariate normality
```{r}
mvn(cor_data, mvnTest = "mardia")
```

# function for f2
```{r}
f2_func = function(r2) {
  den = 1 - r2
  return(r2/den)
}
```

# 3-way interaction model
```{r}
three_model = lm(PSOC_avg_z ~ PHQ9_total_z*SSQSR_SatisfactionAvg_z*childAge_z + numChildren_z + HouseholdIncome_z + country, data = df2)
summary(three_model)
```

## normality of residuals
```{r}
## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(three_model)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)
```

## homoscedasticiity
```{r}
 
mod_simple_fitted <- fitted(three_model)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

```

## vif
```{r}
# multicolleniarity
## compute VIF
vif(three_model) 


## compute average VIF
mean(vif(three_model))

## compute tolerance
1 / vif(three_model)
```

# Parent mental health

## PHQ9
```{r}

ggplot(df, aes(x = PHQ9_total, y = PSOC_avg)) +
  geom_point() +
  geom_smooth (method = "lm")

phq = lm(PSOC_avg_z ~ PHQ9_total_z, data = df)
summary(phq)

par(mfrow = c(2, 2))
plot(phq)

psoc_phq = ggplot(df, aes(x = PHQ9_total_z, y = PSOC_avg_z)) +
  geom_point() +
  geom_smooth(method = "lm")
psoc_phq

f2_func(0.1113) ##0.1252391

# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(phq)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(phq)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# generate diagnostic plots
plot(phq)

# to get both standardized and unstandardized coefficients without first having to standardize variables

# estimate standardized regression coefficients AND the project required
# APA formated regression table

library(apaTables)
apa.reg.table(phq, filename = "draft_apa_regresssion_table.doc")

# independence
# run the Durbin-Watson test

library(pastecs)
library(psych)
library(car)

durbinWatsonTest(phq)

```



# social support

## total
```{r}
social_total = lm(PSOC_avg_z ~ SSQSR_total_z, data = df)
summary(social_total)

par(mfrow = c(2, 2))
plot(social_total)

psoc_ssqr2 = ggplot(df, aes(x = SSQSR_total_z, y = PSOC_avg_z)) +
  geom_point() +
  geom_smooth(method = "lm")
psoc_ssqr2

f2_func(0.01247) ##0.01262746

# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(social_total)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(social_total)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# generate diagnostic plots
plot(social_total)


# independence
# run the Durbin-Watson test

library(pastecs)
library(psych)
library(car)

durbinWatsonTest(social_total)
```


## satisfaction
```{r}
social_satisfaction = lm(PSOC_avg_z ~ SSQSR_satisfaction_z, data = df)
summary(social_satisfaction)

par(mfrow = c(2, 2))
plot(social_satisfaction)

psoc_ssqr = ggplot(df, aes(x = SSQSR_satisfaction_z, y = PSOC_avg_z)) +
  geom_point() +
  geom_smooth(method = "lm")
psoc_ssqr

f2_func(0.07133) ##0.07680877

# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(social_satisfaction)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(social_satisfaction)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")


# to get both standardized and unstandardized coefficients without first having to standardize variables

# estimate standardized regression coefficients AND the project required
# APA formated regression table

library(apaTables)
apa.reg.table(phq, filename = "draft_apa_regresssion_table.doc")

# independence
# run the Durbin-Watson test

library(pastecs)
library(psych)
library(car)

durbinWatsonTest(social_satisfaction)
```

# child age
```{r}
child_age = lm(PSOC_avg_z ~ childage_z, data = df)
summary(child_age)

par(mfrow = c(2, 2))
plot(child_age)

psoc_age = ggplot(df, aes(x = childage_z, y = PSOC_avg_z)) +
  geom_point() +
  geom_smooth(method = lm)
psoc_age

# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(child_age)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(child_age)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(child_age)
```

# Interactions

## child age with social support total --  do not report it as significant -- because it is very small effect size -- or report exactly what is happening
```{r}
process(data = df, y = "PSOC_avg_z", x = "SSQSR_total_z", w = "childage_z", cov = c("SSQSR_satisfaction_z"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903)

interact_plot(model = lm(PSOC_avg_z ~ SSQSR_total_z*childage_z + SSQSR_satisfaction_z, data = df), pred = SSQSR_total_z, modx = childage_z) 

f2_func(0.0427) ##0.04460462

# check to see if overall model is sig and whether interaction improves fit
int_fit <- lm(PSOC_avg_z ~ SSQSR_total_z*childage_z, data = df)
main_fit <- lm(PSOC_avg_z ~ SSQSR_total_z+childage_z, data = df)
anova(main_fit,int_fit)


model1 = lm(PSOC_avg_z ~ SSQSR_total_z*childage_z + SSQSR_satisfaction_z, data = df)
summary
# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(model1)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(model1)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(model1)

# multicolleniarity
## compute VIF
vif(model1)

## compute average VIF
mean(vif(model1))

## compute tolerance
1 / vif(model1)

```

## child age with social support satisfaction - mean center the variables.
```{r}
process(data = df, y = "PSOC_avg_z", x = "SSQSR_satisfaction_z", w = "childage_z", model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903)

model2 = lm(PSOC_avg_z ~ SSQSR_satisfaction_z*childage_z, data = df)
# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(model2)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(model2)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(model2)

# multicolleniarity
library(car)
## compute VIF
vif(model2)

## compute average VIF
mean(vif(model2))

## compute tolerance
1 / vif(model2)
```

## child age with depression
```{r}
process(data = df, y = "PSOC_avg_z", x = "PHQ9_total_z", w = "childage_z", model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903)

interact_plot(model = lm(PSOC_avg_z ~ PHQ9_total_z*childage_z, data = df), pred = PHQ9_total_z, modx = childage_z) 


f2_func(0.1401) ##0.1629259

# check to see if overall model is sig and whether interaction improves fit
int_fit <- lm(PSOC_avg_z ~ PHQ9_total_z*childage_z, data = df)
main_fit <- lm(PSOC_avg_z ~ PHQ9_total_z+childage_z, data = df)
anova(main_fit,int_fit)

model3 = lm(PSOC_avg_z ~ PHQ9_total_z*childage_z, data = df)
# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(model3)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(model3)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(model3)

# multicolleniarity
## compute VIF
vif(model3)

## compute average VIF
mean(vif(model3)) 

## compute tolerance
1 / vif(model3)
```

## depression and social support total
```{r}
process(data = df, y = "PSOC_avg_z", x = "PHQ9_total_z", w = "SSQSR_total_z", model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903)

model4 = lm(PSOC_avg_z ~ PHQ9_total_z*SSQSR_total_z, data = df)
summary(model4)
# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(model4)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(model4)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(model4)

# multicolleniarity
## compute VIF
vif(model4)

## compute average VIF
mean(vif(model4)) 

## compute tolerance
1 / vif(model4)
```

## depression and social support satisfaction
```{r}
model5 = lm(PSOC_avg_z ~ SSQSR_satisfaction_z*childage_z, data = df)
# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(model5)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(model5)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(model5)

# multicolleniarity
## compute VIF
vif(model5)

## compute average VIF
mean(vif(model5)) 

## compute tolerance
1 / vif(model5)
```

## 3-way interaction
```{r}
process(data = df, y = "PSOC_avg_z", x = "PHQ9_total_z", w = "SSQSR_total_z", z = "childage_z", model = 3, jn = 1, 
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903, plot = 1) 

## not significant

fita3 <- lm(PSOC_avg_z ~ PHQ9_total_z * SSQSR_total_z * childage_z, data = df)

probe_interaction(fita3, pred = PHQ9_total_z, modx = SSQSR_total_z, mod2 = childage_z,
                  alpha = .1)

f2_func(0.1716) ##0.2071463

model6 = lm(PSOC_avg_z ~ SSQSR_total_z*PHQ9_total_z*childage_z, data = df)
# looking at residuals

## extract the model residuals while maintaining the original scale
mod_simple_resid <- residuals(model6)

## histogram of model residuals in the original scale
hist(mod_simple_resid, main = "", 
     #ylim = c(0, .9), # set the lower and upper values for the graph
     xlab = "Model Residuals (z-score)", col = "beige", probability = TRUE)
curve(dnorm(x, mean = mean(mod_simple_resid), 
            sd = sd(mod_simple_resid)), col = "darkgreen",
            add = TRUE, lwd = 2)

# looking at homoscedasticity
mod_simple_fitted <- fitted(model6)

## scatterplot of residuals ~ predicted values
plot(mod_simple_resid ~ mod_simple_fitted,
     pch = 16, # sets the Point CHarater to filled in circles
     ylab = "Model Residuals",
     xlab = "Model Predicted Values")
## horizontal line at expected mean value of residuals
abline(h = 0, lwd = 2, col = "blue")
## lines at +/- 2SD from mean to provide visual indication of equal variance
abline(h = (sd(mod_simple_resid)*2), lty = 3, lwd = 1.5, col = "red")
abline(h = (sd(mod_simple_resid)*-2), lty = 3, lwd = 1.5, col = "red")

# independence
durbinWatsonTest(model6)

# multicolleniarity
## compute VIF
vif(model6)

## compute average VIF
mean(vif(model6)) 

## compute tolerance
1 / vif(model6)
```

# APA-ish tables

```{r apa_table}
tab_model(main_fit, int_fit,
          show.std = TRUE,
          #pred.labels = c("intercept","PHQ-9","Child age","PHQ-9 * Age"),
          col.order = c("est","p","ci","std.est","std.p"),
          p.style = "numeric",
          file = "draft_dep_by_age.html")
```

