---
title: "FINAL"
author: "Maitri Jain"
date: '2023-02-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library and data
```{r}
library(tidyverse)
library(Hmisc)
library(psych)
library(interactions)
library(corrplot)
library(sjPlot)
library(cowplot)
library(broom.mixed)

###source("../../ISDP:SRCD 2022/R_Scripts/processv41/PROCESS v4.1 for R/process.R") 
df = read_csv("../data/PSOC_final_data.csv")

# Standardizing
df$PSOC_avg_z <- as.numeric(scale(df$PSOC_avg, center = TRUE, scale = TRUE))
df$PHQ9_total_z <- as.numeric(scale(df$PHQ9_total, center = T, scale = T))
df$SSQSR_SatisfactionAvg_z <- as.numeric(scale(df$SSQSR_SatisfactionAvg, center = T, scale = T))
df$childAge_z <- as.numeric(scale(df$childAge, center = T, scale = T))
df$numChildren_z <- as.numeric(scale(df$numChildren, center = T, scale = T))
df$HouseholdIncome_z <- as.numeric(scale(df$HouseholdIncome, center = T, scale = T)) 
df$SSQSR_Total_z <- as.numeric(scale(df$SSQSR_Total, center = T, scale = T))
df2 = df %>% drop_na(country)


df_total = df2 %>% select("PSOC_avg", "SSQSR_Total", "childAge", "PHQ9_total", "numChildren", "HouseholdIncome", "country")

df_satisfaction = df2 %>% select("PSOC_avg", "SSQSR_SatisfactionAvg", "childAge", "PHQ9_total", "numChildren", "HouseholdIncome", "country")
```

# Looking at demographics
```{r}
# Country
table(df$country)
g <- df2 %>%
  group_by(country) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))


# Child Age
describe(df2$childAge)

# Race
summary(as.factor(df$ParentRace_string))
g <- df2 %>%
  group_by(ParentRace_string) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# Ethnicity
summary(as.factor(df$ParentLatinx))
g <- df2 %>%
  group_by(ParentLatinx) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# Income
summary(as.factor(df$HouseholdIncome))
g <- df2 %>%
  group_by(HouseholdIncome) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# Education
summary(as.factor(df$ParentEducation_string))
g <- df2 %>%
  group_by(ParentEducation_string) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# Number of children
describe(df2$numChildren)

# Relationship Status
summary(as.factor(df$Married))
g <- df2 %>%
  group_by(Married) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))
g

# Parent gender
summary(as.factor(df$parentGender_chr))
g <- df2 %>%
  group_by(parentGender_chr) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))


# Parent age
describe(df2$ParentAge)

# Child Race
summary(as.factor(df$ChildRace_string))
g <- df2 %>%
  group_by(ChildRace_string) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# Child Gender
summary(as.factor(df$childGender_chr))
g <- df2 %>%
  group_by(childGender_chr) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# Child ethnicity
summary(as.factor(df$ChildLatinx))
g <- df2 %>%
  group_by(ChildLatinx) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))

# PSOC
summary(df$PSOC_avg_z)
ggplot(df, aes(x = PSOC_avg_z)) + geom_histogram()
shapiro.test(df$PSOC_avg_z) # normal

# PHQ
summary(df$PHQ9_total_z)
ggplot(df, aes(x = PHQ9_total_z)) + geom_histogram()
shapiro.test(df$GAD_total_z) # not normal

# Social support total
summary(df$SSQSR_Total_z)
ggplot(df, aes(x = SSQSR_Total_z)) + geom_histogram()
shapiro.test(df$SSQSR_Total_z) # not normal

# Social support satisfaction
summary(as.numeric(df$SSQSR_SatisfactionAvg_z))
ggplot(df, aes(x = as.numeric(df$SSQSR_SatisfactionAvg_z))) + geom_histogram()
shapiro.test(as.numeric(df$SSQSR_SatisfactionAvg_z)) # not normal

```

# Differences in variable based on country
```{r}

#child age -- age of children less in the USA
g <- ggplot(df, aes(country, childAge)) +
  geom_boxplot()
g

res_aov <- aov(childAge ~ country,
  data = df2
)
summary(res_aov)

TukeyHSD(res_aov)

#income -- USA higher income
g <- ggplot(df, aes(country, HouseholdIncome)) +
  geom_boxplot()
g

res_aov <- aov(HouseholdIncome ~ country,
  data = df2
)
summary(res_aov)

TukeyHSD(res_aov)

#number of children -- no difference
g <- ggplot(df, aes(country, numChildren)) +
  geom_boxplot()
g

res_aov <- aov(numChildren ~ country,
  data = df2
)
summary(res_aov)

TukeyHSD(res_aov)

#parent age -- no difference
g <- ggplot(df, aes(country, ParentAge)) +
  geom_boxplot()
g

res_aov <- aov(ParentAge ~ country,
  data = df2
)
summary(res_aov)

TukeyHSD(res_aov)

#Parent race --  significant difference
chisq.test(df2$country, df2$ParentRace_string, correct=FALSE)

g <- df2 %>%
  group_by(country,ParentRace_string) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))
g

#Parent ethnicity -- no difference
chisq.test(df2$country, df2$ParentLatinx, correct=FALSE)


#parent education -- significant difference
chisq.test(df2$country, df2$ParentEducation_string, correct=FALSE)

#Parent gender -- no difference
chisq.test(df2$country, df2$ParentGender, correct=FALSE)

#child race -- significant difference
chisq.test(df2$country, df2$ChildRace_string, correct=FALSE)

g <- df %>%
  group_by(country,ChildRace_string) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))
g

# child ethnicity -- significant difference
chisq.test(df2$country, df2$ChildLatinx, correct=FALSE)

g <- df %>%
  group_by(country,ChildLatinx) %>%
  summarise(cnt = n()) %>%
  mutate(freq = formattable::percent(cnt / sum(cnt))) %>% 
  arrange(desc(freq))
g

#child gender  -- no significant difference
chisq.test(df2$country, df2$childGender_chr, correct=FALSE)


#PSOC -- USA higher PSOC (0.37 SD)
g <- ggplot(df, aes(country, PSOC_avg_z)) +
  geom_boxplot()
g

res_aov <- aov(PSOC_avg_z ~ country,
  data = df2
)
summary(res_aov)

TukeyHSD(res_aov)

#PHQ -- no difference
g <- ggplot(df, aes(country, PHQ9_total_z)) +
  geom_boxplot()
g

res_aov <- aov(PHQ9_total_z ~ country,
  data = df2
)
summary(res_aov)

TukeyHSD(res_aov)

#Social support satisfaction -- no difference
g <- ggplot(df, aes(country, SSQSR_SatisfactionAvg_z)) +
  geom_boxplot()
g

res_aov <- aov(SSQSR_SatisfactionAvg_z ~ country,
  data = df
)
summary(res_aov)

TukeyHSD(res_aov)


#Social support total -- no difference
g <- ggplot(df, aes(country, SSQSR_Total_z)) +
  geom_boxplot()
g

res_aov <- aov(SSQSR_Total_z ~ country,
  data = df
)
summary(res_aov)

TukeyHSD(res_aov)


```

# Calculating internal reliabilities
```{r}
# PSOC
psoc_df = df2 %>% select("PSOC_1", "PSOC_2R", "PSOC_3R", "PSOC_4R", "PSOC_5R", "PSOC_6", "PSOC_7", "PSOC_8R", "PSOC_9R", "PSOC_10", "PSOC_11", "PSOC_12R", "PSOC_13", "PSOC_14R", "PSOC_15", "PSOC_16R", "PSOC_17")
omega = omega(psoc_df,n.obs=207,title = "Omega")
omega$omega.tot

# PHQ-9
phq_df = df2 %>% select("PHQ_1", "PHQ_2", "PHQ_3", "PHQ_4", "PHQ_5", "PHQ_6", "PHQ_7", "PHQ_8", "PHQ_9")
omega = omega(phq_df,n.obs=206,title = "Omega")
omega$omega.tot

##SSQSR Satisfaction
ssqsr_df = df2 %>% select("SSQSR_1Satisfaction", "SSQSR_2Satisfaction", "SSQSR_3Satisfaction", "SSQSR_4Satisfaction", "SSQSR_5Satisfaction", "SSQSR_6Satisfaction")
omega = omega(ssqsr_df,n.obs=206,title = "Omega")
omega$omega.tot

##SSQSR Total
ssqsr_total_df = df2 %>% select("SSQSR_HelpNum", "SSQSR_RelaxNum", "SSQSR_AcceptNum", "SSQSR_CareNum", "SSQSR_BetterNum", "SSQSR_ConsoleNum")
omega = omega(ssqsr_total_df,n.obs=207,title = "Omega")
omega$omega.tot

```

# Descriptive correlations
```{r}
cor_data = df2 %>% select("PHQ9_total", "SSQSR_SatisfactionAvg", "SSQSR_Total", "PSOC_avg", "childAge", "numChildren", "HouseholdIncome")

# correlations between variables
correlations = rcorr(as.matrix(cor_data))

colnames(correlations$r) <- c("Parent Depression", "Social Support Satisfaction", "Social Support Number", "PSOC", "Child Age", "Number of Children", "Household Income")
rownames(correlations$r) <- c("Parent Depression", "Social Support Satisfaction", "Social Support Number", "PSOC", "Child Age", "Number of Children", "Household Income")

corrplot(correlations$r, method = "color", type = "lower", diag = FALSE, outline = TRUE, tl.col = "black", tl.srt = 30, addCoef.col = TRUE, number.cex = 0.7) 

# table
tab_corr(
correlations$r,
wrap.labels = 40,
show.p = TRUE,
p.numeric = FALSE,
digits = 2,
triangle = "lower",
var.labels = c("PHQ9", "SSQSR Satisfaction", "SSQSR Number", "PSOC", "Child Age", "Number of Children", "Income"),
file = "corr.html"
)
```

# Direct effects


## covariates
```{r}
#income
summary(lm(PSOC_avg ~ HouseholdIncome, data = df))
summary(lm(scale(PSOC_avg) ~ scale(HouseholdIncome), data=df))

#children
summary(lm(PSOC_avg ~ numChildren, data = df))
summary(lm(scale(PSOC_avg) ~ scale(numChildren), data=df))
```

## PHQ
```{r}
# total
summary(lm(PSOC_avg ~ PHQ9_total + HouseholdIncome + numChildren, data = df)) #negative association
summary(lm(scale(PSOC_avg) ~ scale(PHQ9_total) + scale(HouseholdIncome) + scale(numChildren), data = df)) 

#functioning
summary(lm(PSOC_avg ~ PHQ_Functioning + HouseholdIncome + numChildren, data = df)) ## more difficulties with functioning associated with lower PSOC
summary(lm(scale(PSOC_avg) ~ scale(PHQ_Functioning) + scale(HouseholdIncome) + scale(numChildren), data = df))

#severity
df = df %>% mutate(
  PHQ9_severity_num = recode(
    PHQ9_severity, 
    'none' = 0,
    'mild' = 1,
    'moderate' = 2,
    'modSev' = 3,
    'severe' = 4
  )
)

summary(lm(PSOC_avg ~ PHQ9_severity_num + HouseholdIncome + numChildren + ParentEducation_string, data = df)) ## higher severity associated with lower PSOC
```

## Social support
```{r}
# number
summary(lm(PSOC_avg ~ SSQSR_Total + HouseholdIncome + numChildren, data = df)) # no association
summary(lm(scale(PSOC_avg) ~ scale(SSQSR_Total) + scale(HouseholdIncome) + scale(numChildren), data = df))

# satisfaction
summary(lm(PSOC_avg ~ SSQSR_SatisfactionAvg + HouseholdIncome + numChildren, data = df)) # positive association
summary(lm(scale(PSOC_avg) ~ scale(SSQSR_SatisfactionAvg) + scale(HouseholdIncome) + scale(numChildren), data = df))
```

## Child Age
```{r}
summary(lm(PSOC_avg ~ childAge + HouseholdIncome + numChildren, data = df)) # not associated
summary(lm(scale(PSOC_avg) ~ scale(childAge) + scale(HouseholdIncome) + scale(numChildren), data = df))
```

# Interactions

## Social support with child age
```{r}
# number

process(data = df, y = "PSOC_avg", x = "SSQSR_Total", w = "childAge", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, seed = 2903)

## standardized
process(data = df, y = "PSOC_avg_z", x = "SSQSR_Total_z", w = "childAge_z", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903, stand = TRUE) # no significant interaction


# satisfaction
process(data = df, y = "PSOC_avg", x = "SSQSR_SatisfactionAvg", w = "childAge", cov = c("HouseholdIncome", "numChildren", "ParentEducation_string"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903) # no significant interaction
```

## Depression with child age
```{r}
# total
process(data = df, y = "PSOC_avg", x = "PHQ9_total", w = "childAge", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903)

process(data = df, y = "PSOC_avg", x = "PHQ9_total", w = "childAge", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, seed = 2903)

# functioning
process(data = df, y = "PSOC_avg", x = "PHQ_Functioning", w = "childAge", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903) 

```

## Depression with social support
```{r}
# total with total
process(data = df, y = "PSOC_avg", x = "PHQ9_total", w = "SSQSR_Total", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903) #no

## standardized
process(data = df, y = "PSOC_avg_z", x = "PHQ9_total_z", w = "SSQSR_Total_z", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903)

# total with functioning
process(data = df, y = "PSOC_avg", x = "PHQ_Functioning", w = "SSQSR_Total", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903) 

# satisfaction with total
process(data = df, y = "PSOC_avg", x = "PHQ9_total", w = "SSQSR_SatisfactionAvg", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903) 


# satisfaction with functioning
process(data = df, y = "PSOC_avg", x = "PHQ9_total", w = "SSQSR_SatisfactionAvg", cov = c("HouseholdIncome", "numChildren"), model = 1, jn = 1,
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903) 


```

## 3-way interaction
```{r}

# depression total and social support satisfaction
# HERE 
process(data = df, y = "PSOC_avg", x = "SSQSR_SatisfactionAvg", w = "childAge", z = "PHQ9_total", cov = c("HouseholdIncome", "numChildren", "country"), model = 3, jn = 1, 
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903, plot = 1) ##significant

process(data = df, y = "PSOC_avg", x = "SSQSR_SatisfactionAvg", w = "childAge", z = "PHQ9_total", cov = c("HouseholdIncome", "numChildren"), model = 3, jn = 1, 
         boot = 5000, modelbt = 1,
         moments = 1, seed = 2903)

## with standardization
process(data = df, y = "PSOC_avg_z", x = "SSQSR_SatisfactionAvg_z", w = "childAge_z", z = "PHQ9_total_z", cov = c("HouseholdIncome_z", "numChildren_z"), model = 3, jn = 1, 
         boot = 5000, modelbt = 1,
         moments = 1, seed = 2903, plot = 1) 


# simple slopes
sim_slopes(
  model = lm(PSOC_avg ~ PHQ9_total*SSQSR_SatisfactionAvg*childAge, data = df),
  pred = SSQSR_SatisfactionAvg,
  modx = childAge,
  mod2 = PHQ9_total
) 

# depression total and social suppoort number
process(data = df, y = "PSOC_avg", x = "SSQSR_Total", w = "childAge", z = "PHQ9_total", cov = c("HouseholdIncome", "numChildren"), model = 3, jn = 1, 
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903, plot = 1) 

## Standardized
process(data = df, y = "PSOC_avg_z", x = "SSQSR_Total_z", w = "childAge_z", z = "PHQ9_total_z", cov = c("HouseholdIncome", "numChildren"), model = 3, jn = 1, 
         boot = 5000, modelbt = 1,
         moments = 1, center = 2, seed = 2903, plot = 1) 


#using lm


three_model <- lm(PSOC_avg ~ scale(SSQSR_Total)*scale(childAge)*scale(PHQ9_total) + scale(numChildren) + scale(HouseholdIncome) + country, data = df_total)
summary(three_model)

three_model_2_ns <- lm(PSOC_avg ~ SSQSR_Total*childAge*PHQ9_total + numChildren + HouseholdIncome + country, data = dff_sstotal)
summary(three_model_2_ns)

tab_model(three_model,bootstrap = TRUE,iterations = 5000,seed = 209,
          file = "total_three_way.html")

two_model <- lm(PSOC_avg ~ scale(PHQ9_total)*scale(SSQSR_Total) +
                               scale(SSQSR_Total)*scale(childAge) + 
                               scale(PHQ9_total)*scale(childAge) + scale(numChildren) + scale(HouseholdIncome) + country, data = df_total)
summary(two_model)

one_model <- lm(PSOC_avg ~ scale(PHQ9_total) +
                               scale(SSQSR_Total) + 
                               scale(childAge) + scale(numChildren) + scale(HouseholdIncome) + country, data = df_total)
summary(one_model)

tab_model(two_model,bootstrap = TRUE,iterations = 5000,seed = 209,
          file = "total_two_way.html")

anova_result = anova(three_model, two_model)
anova_result

anova_result = anova(two_model, one_model)
anova_result

## calculated JN and simple slopes
two_model_total <- lm(PSOC_avg ~ SSQSR_Total*childAge + numChildren + HouseholdIncome + country, data = df_total)

sim_results <- sim_slopes(two_model_total, pred =SSQSR_Total, modx = childAge, jnplot = TRUE, digits = 5)
sim_results

two_model_depression = lm (PSOC_avg ~ PHQ9_total*childAge + numChildren + HouseholdIncome + country, data = df_total)


sim_results_dep <- sim_slopes(two_model_depression, pred = PHQ9_total, modx = childAge, jnplot = TRUE, digits = 5)
sim_results_dep

# Customize axis titles in the plot
sim_results_plot <- plot(sim_results, ylab = "Slope of Social Support Satisfaction", xlab = "Child Age")
sim_results_plot

sim_slopes(model = two_model_total, pred =SSQSR_Total, modx = childAge, jnplot = TRUE, ylab = "Slope of Social Support Total", xlab = "Child Age")


plot = ggplot2

sim_slopes(model = two_model_depression, pred =PHQ9_total, modx = childAge, jnplot = TRUE, ylab = "Slope of Parent Depression", xlab = "Child Age")
```


# Plots

## interactions

### PHQ9
```{r}

interact_plot(model = lm(PSOC_avg ~ PHQ9_total*childAge + numChildren + HouseholdIncome, data = df), pred = PHQ9_total, modx = childAge)

sim_slopes(
  model = lm(PSOC_avg ~ PHQ9_total*childAge+ + numChildren + HouseholdIncome, data = df),
  pred = PHQ9_total,
  modx = childAge,
) 

```

### SSQSR
```{r}
# simple slopes
sim_slopes(
  model = lm(PSOC_avg ~ SSQSR_Total*childAge+ SSQSR_SatisfactionAvg + numChildren + HouseholdIncome, data = df),
  pred = SSQSR_Total,
  modx = childAge,
) 

interact_plot(model = lm(PSOC_avg ~ SSQSR_Total*childAge+ SSQSR_SatisfactionAvg + numChildren + HouseholdIncome, data = df), pred = SSQSR_Total, modx = childAge)

```

### 3-way
```{r}
# PHQ9 total
interact_plot(model = lm(PSOC_avg ~ PHQ9_total*SSQSR_SatisfactionAvg*childAge + numChildren + HouseholdIncome, data = df), pred =SSQSR_SatisfactionAvg , modx = childAge, mod2 = PHQ9_total, alpha = .05, plot.points = TRUE, interval = TRUE, int.type = "confidence", x.label = "Social Support Satisfaction", y.label = "PSOC", mod2.labels = c("PHQ9: -1 SD",  "PHQ9: Mean", "PHQ9: +1 SD"), legend.main = "Child Age", colors = c("#F8766D", "#619CFF", "#7CAE00"))
```

# JN Plots
```{r}

three_model <- lm(PSOC_avg ~ scale(SSQSR_SatisfactionAvg)*scale(childAge)*scale(PHQ9_total) + scale(numChildren) + scale(HouseholdIncome) + country, data = df)
summary(three_model) 

two_model <- lm(PSOC_avg ~ scale(PHQ9_total)*scale(SSQSR_SatisfactionAvg) +
                               scale(SSQSR_SatisfactionAvg)*scale(childAge) + 
                               scale(PHQ9_total)*scale(childAge) + scale(numChildren) + scale(HouseholdIncome) + country, data = df_satisfaction)
summary(two_model)



tab_model(three_model,bootstrap = TRUE,iterations = 5000,seed = 209,
          file = "satisfaction_three_way.html")


tab_model(two_model,bootstrap = TRUE,iterations = 5000,seed = 209,
          file = "satisfaction_two_way.html")

anova_result = anova(two_model, three_model)
anova_result



# Residual standard error: 0.4318 on 194 degrees of freedom
#   (11 observations deleted due to missingness)
# Multiple R-squared:  0.2455,	Adjusted R-squared:  0.2066 
# F-statistic: 6.311 on 10 and 194 DF,  p-value: 2.301e-08

# Estimate and plot interaction effects using sim_slopes

three_model2 <- lm(PSOC_avg ~ SSQSR_SatisfactionAvg*childAge*PHQ9_total + numChildren + HouseholdIncome + country, data = df_satisfaction)

sim_results <- sim_slopes(three_model2, pred =SSQSR_SatisfactionAvg, modx = childAge, mod2 = PHQ9_total, jnplot = TRUE)
sim_results

# Customize axis titles in the plot
sim_results_plot <- plot(sim_results, ylab = "Slope of Social Support Satisfaction", xlab = "Child Age")
sim_results_plot

threeway_plot = sim_slopes(model = three_model2, pred =SSQSR_SatisfactionAvg, modx = childAge, mod2 = PHQ9_total, jnplot = TRUE, ylab = "Slope of Social Support Satisfaction", xlab = "Child Age")

```

# Predictions
```{r}



# model
model_stan = lm(PSOC_avg_z ~ PHQ9_total_z*SSQSR_SatisfactionAvg_z*childAge_z + numChildren_z + HouseholdIncome_z + country, data = df)

prediction_df = expand.grid(PHQ9_total_z = c(-1, 0, +1),
                            SSQSR_SatisfactionAvg_z = seq(min(df$SSQSR_SatisfactionAvg_z, na.rm = TRUE), max(df$SSQSR_SatisfactionAvg_z, na.rm = TRUE), length.out = 24),
                            childAge_z = c(-1, 0, +1),
                            numChildren_z = mean(df$numChildren_z),
                            HouseholdIncome_z = mean(df$HouseholdIncome_z),
                            country = ("USA")
                            )



predictions = data.frame(predict(object = model_stan, newdata = prediction_df, interval = 'confidence')) %>% 
  cbind(prediction_df, .) 

# Create the plot

plot = ggplot(predictions, aes(x = SSQSR_SatisfactionAvg_z, y = fit)) +
  geom_point(data = df, aes(x = SSQSR_SatisfactionAvg_z, y = PSOC_avg_z, color = as.factor(predictions$childAge_z)), alpha = 0.5) +
  geom_line(aes(color = as.factor(predictions$childAge_z))) +
 geom_ribbon(aes(ymin = lwr, ymax = upr, fill = as.factor(predictions$childAge_z)), alpha = 0.3) +
  facet_grid(cols = vars(as.factor(predictions$PHQ9_total_z))) +
  ylab('Estimated PSOC\n(Standardized)') +
  xlab('Social Support Satisfaction (Standardized)') +
  theme_bw() +
  labs(color = 'Child Age', fill = 'Child Age') +
  scale_fill_discrete(labels=c('-1 SD', 'Mean', ' +1 SD')) +
  scale_color_discrete(labels=c('-1 SD', 'Mean', ' +1 SD')) +
  ggtitle("Depression levels (SD)") +
  theme(plot.title = element_text(size = 12, hjust = 0.5))

plot

plot_grid(plot, threeway_plot$jnplot, labels = c("A", "B"), nrow = 1, ncol = 2)

```

# 2-way interaction predictions plot
```{r}

# model
model_stan2 = lm(PSOC_avg_z ~ SSQSR_Total_z*childAge_z + numChildren_z + HouseholdIncome_z + country, data = df)

prediction_df2 = expand.grid(PHQ9_total_z = c(-1, 0, +1),
                            SSQSR_Total_z = seq(min(df$SSQSR_Total_z, na.rm = TRUE), max(df$SSQSR_Total_z, na.rm = TRUE), length.out = 24),
                            childAge_z = c(-1, 0, +1),
                            numChildren_z = mean(df$numChildren_z),
                            HouseholdIncome_z = mean(df$HouseholdIncome_z),
                            country = ("USA")
                            )



predictions2 = data.frame(predict(object = model_stan2, newdata = prediction_df2, interval = 'confidence')) %>% 
  cbind(prediction_df2, .)


# Create the plot

plot = ggplot(predictions2, aes(x = SSQSR_Total_z, y = fit)) +
  geom_point (data = df, aes(x = SSQSR_Total_z, y = PSOC_avg_z, color = as.factor(predictions2$childAge_z)), alpha = 0.5) +
  geom_line(aes(color = as.factor(predictions2$childAge_z))) +
  geom_ribbon(aes(ymin = lwr, ymax = upr, fill = as.factor(predictions2$childAge_z)), alpha = 0.3) +
  ylab('Estimated PSOC\n(Standardized)') +
  xlab('Social Support Total (Standardized)') +
  theme_bw() +
  labs(color = 'Child Age', fill = 'Child Age') +
  scale_fill_discrete(labels=c('-1 SD', 'Mean', ' +1 SD')) +
  scale_color_discrete(labels=c('-1 SD', 'Mean', ' +1 SD')) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))

plot


# for depression and child age interaction

## model
model_dep = lm(PSOC_avg_z ~ PHQ9_total_z*childAge_z + numChildren_z + HouseholdIncome_z + country, data = df)

prediction_dep = expand.grid(PHQ9_total_z = c(-1, 0, +1),
                            SSQSR_Total_z = seq(min(df$SSQSR_Total_z, na.rm = TRUE), max(df$SSQSR_Total_z, na.rm = TRUE), length.out = 24),
                            childAge_z = c(-1, 0, +1),
                            numChildren_z = mean(df$numChildren_z),
                            HouseholdIncome_z = mean(df$HouseholdIncome_z),
                            country = ("USA")
                            )



predictions_dep = data.frame(predict(object = model_dep, newdata = prediction_dep, interval = 'confidence')) %>% 
  cbind(prediction_dep, .)

## create the plot

plot_dep = ggplot(predictions_dep, aes(x = PHQ9_total_z, y = fit)) +
  geom_point (data = df, aes(x = PHQ9_total_z, y = PSOC_avg_z, color = as.factor(predictions_dep$childAge_z)), alpha = 0.5) +
  geom_line(aes(color = as.factor(predictions_dep$childAge_z))) +
  geom_ribbon(aes(ymin = lwr, ymax = upr, fill = as.factor(predictions_dep$childAge_z)), alpha = 0.3) +
  ylab('Estimated PSOC\n(Standardized)') +
  xlab('Parent Depressive Symptoms (Standardized)') +
  theme_bw() +
  labs(color = 'Child Age', fill = 'Child Age') +
  scale_fill_discrete(labels=c('-1 SD', 'Mean', ' +1 SD')) +
  scale_color_discrete(labels=c('-1 SD', 'Mean', ' +1 SD')) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))

plot_dep

plot_grid(plot, sim_results$jnplot, plot_dep, sim_results_dep$jnplot, labels = c("A", "B", "C", "D"), axis = "bottom")


```